---
title: "Quizz - Practice Loops"
author: "Billy"
date: "2023-11-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Practice Loops
The first section of code provides you with the different loops used for the practice quiz. Make note that each loop is encapsulated in a function for easy reuse. After finishing the quiz feel free to the loops yourself to explore use-cases.

```{r "loop creation"}
# For loop 1
for_1 <- function (x) {
  y <- c()
  for (i in 1:length(x)) {
    y <- c(y, i)
  }
  return(y)
}

for_1(1:10)
for_1(letters)

# For loop 2
for_2 <- function (x) {
  y <- c()
  for (i in x) {
    y <- c(y, i)
  }
  return(y)
}

for_2(1:10)
for_2(letters)

# While loop 1
while_1 <- function (x, i, z) {
  y <- c()
  while(i < z) {
    y <- c(y, x[i])
    i <- i + 1
  }
}

# For loop 3
for_3 <- function(x, z) {
  y <- c()
  for (i in x) {
    if (i == z) {
      break
    }
    y <- c(y, i)
  }
  return(y)
}

for_3(1:30, 18)
for_3(letters, 10)

# For loop 4
for_4 <- function(x, z) {
  y <- c()
  for (i in x) {
    if (i == z) {
      return(y)
    }
    y <- c(y, i)
  }
  return(-1)
}

for_4(1:30, 18)
for_4(letters, 10)

# For loop 5
for_5 <- function(x, z) {
  y <- c()
  for (i in x) {
    if (i == z) {
      next
    }
    y <- c(y, i)
  }
  return(y)
}

for_5(1:30, 18)
for_5(letters, "f")

```

Below you find the function call to each loop. Use different function names (e.g., for_1, while_1) and arguments to answer the quiz questions.
```{r "loop call"}
# Try out different function calls for the loops below...
for_4(letters, 10)
```
