---
title: "Quizz - Practice Conditionals"
author: "Billy"
date: "2023-11-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Practice Conditionals

The first section of code provides you with the different conditionals used for the practice quiz. Make note that each conditional is encapsulated in a function for easy reuse. After finishing the quiz feel free to alter the conditionals yourself to explore use-cases.

```{r "conditional creation"}
# Conditional 1
cond_1 <- function(x, y){
  if (x < y) {
    z <- "less than"
  } else if (x > y) {
    z <- "more than"
  } else {
    z <- "equal"
  }
  return(z)
}

cond_1("g", "z")

# Conditional 2
cond_2 <- function(x, y){
  if (x == y) {
    z <- "equal"
  } else {
    z <- "not equal"
  }
  return(z)
}

cond_2("g","z")

# Conditional 3
cond_3 <- function(x, y, relation = "equal"){
  if (relation == "equal") {
    if (x == y) {
     return(TRUE)
    } else {
      return(FALSE)
    }
  } else if (relation == "not") {
    if (x != y) {
     return(TRUE)
    } else {
      return(FALSE)
    }
  } 
}

cond_3("g", "z", "not")

```

Below you find the function call to each conditional. Use different function names (e.g., cond_1, cond_3) and arguments to answer the quiz questions.

```{r "conditional call"}
# Try out the functions for conditionals below...
cond_3("g", "z", "not")
```
